A hidden Active Galactic Nuclei population: the first radio luminosity functions by physical process

### 2024-11-01 src/tex/ms.tex
[showyourwork] overleaf sync

\section*{Data Availability}
All data used in this paper is either publicly available on \href{https://lofar-surveys.org}{https://lofar-surveys.org} or from relevant citations herein, including catalogues, rms images, and star masks. We have prepared this manuscript using using the showyourwork (\href{https://github.com/rodluger/showyourwork}{https://github.com/rodluger/showyourwork}) open source scientific article workflow, first introduced in \cite{luger_mapping_2021}. This ensures complete transparency. The code is available at \hl{update link when ready to publish}. 
\section*{Acknowledgements}
LKM recognizes support from UKRI [MR/T042842/1]. 
RK recognizes support from UK STFC via grant [ST/V000594/1].
PNB recognizes support from UK STFC via grants [ST/V000594/1] and [ST/Y000951/1].
BY thanks the University of Edinburgh and Leiden Observatory for support through the Edinburgh–Leiden joint studentship.
JMGHJdJ recognizes support from project CORTEX (NWA.1160.18.316) of research programme NWA-ORC which is (partly) financed by the Dutch Research Council (NWO). 
FS recognizes support from STFC [ST/Y004159/1]. 
MB and IP recognize support from INAF under the Large Grant 2022 funding scheme (project “MeerKAT and LOFAR Team up: a Unique Radio Window on Galaxy/AGN co-Evolution”).
DJBS recognizes support from UK STFC via grants [ST/V000624/1] and  [ST/Y001028/1].
RJvW recognizes support from ERC Starting Grant ClusterWeb 804208. 
This work was supported by SURF Cooperative grant EINF-6218 and EGI-ACE project (Horizon 2020 grant 101017567).

>>>>

\section*{Data Availability}
All data used in this paper is either publicly available on \href{https://lofar-surveys.org}{https://lofar-surveys.org} or from relevant citations herein, including catalogues, rms images, and star masks.  This study was carried out using showyourwork (\href{https://github.com/showyourwork/showyourwork}{https://github.com/showyourwork/showyourwork}) which is open source scientific article workflow, first introduced in \cite{luger_mapping_2021}. This leverages continuous integration to
programmatically download the data from \href{https://zenodo.org/}{zenodo.org}, create the figures, and compile the manuscript. The code is available at \href{https://github.com/lmorabit/hidden_AGN}{https://github.com/lmorabit/hidden\_AGN} which is linked to the starting datasets for this work, which are hosted on Zenodo with their own DOIs (10.5281/zenodo.14012620, 10.5281/zenodo.14013377, 14013423, 14013439, 14014490, 14014542, 14014849, and 14014853), ensuring complete reproducibility.

\section*{Acknowledgements}
LKM recognizes support from UKRI [MR/T042842/1]. 
RK recognizes support from UK STFC via grant [ST/V000594/1].
PNB recognizes support from UK STFC via grants [ST/V000594/1] and [ST/Y000951/1].
BY thanks the University of Edinburgh and Leiden Observatory for support through the Edinburgh–Leiden joint studentship.
JMGHJdJ recognizes support from project CORTEX (NWA.1160.18.316) of research programme NWA-ORC which is (partly) financed by the Dutch Research Council (NWO). 
FS recognizes support from STFC [ST/Y004159/1]. 
MB and IP recognize support from INAF under the Large Grant 2022 funding scheme (project “MeerKAT and LOFAR Team up: a Unique Radio Window on Galaxy/AGN co-Evolution”).
DJBS recognizes support from UK STFC via grants [ST/V000624/1] and  [ST/Y001028/1].
RJvW recognizes support from ERC Starting Grant ClusterWeb 804208. 
This work was supported by SURF Cooperative grant EINF-6218 and EGI-ACE project (Horizon 2020 grant 101017567).
